### 2024-09-20 Article/main.tex
minima

\begin{definition}[Graph with Equivalence~\cite{concur2006}]
    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes. An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$. Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
\end{definition}

@@

Graphs with equivalences are alternative representation of \emph{quotient graphs} over an equivalence relation. The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.

@@

\begin{proof}
    In order to apply Theorem~\ref{th:crit_for_adh}, we can consider the quotient functor defined in Definition~\ref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$. We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mappend onto monos in $\mathbf{Graph}$. In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
    \todo{Generalizzare il fatto che i limiti in $\mathbf{EqGrph}$ rimangono limiti in $\mathbf{Graph}$} 
\end{proof}

>>>>

\begin{definition}[Graph with Equivalence~\cite{concur2006}]
    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes. An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$. Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
\end{definition}

@@

Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation. The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.

@@

\begin{proof}
    In order to apply Theorem~\ref{th:crit_for_adh}, we can consider the quotient functor defined in Definition~\ref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$. We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$. In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
    \todo{Generalizzare il fatto che i limiti in $\mathbf{EqGrph}$ rimangono limiti in $\mathbf{Graph}$} 
\end{proof}
